---
title: "hw2"
author: "Ali Kolenovic"
date: "9/16/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1
## (i)
## N = 20, 30, 50, 75, 100, respectively
```{r, echo = FALSE}
v1= pbinom(q=8.25, size=20, prob=0.4, lower.tail = T)
v2= pbinom(q=8.25, size=30, prob=0.4, lower.tail = T)
v3= pbinom(q=8.25, size=50, prob=0.4, lower.tail = T)
v4= pbinom(q=8.25, size=75, prob=0.4, lower.tail = T)
v5= pbinom(q=8.25, size=100, prob=0.4, lower.tail = T)

v = c(v1, v2, v3, v4, v5)
v
```

## (ii)
## N = 20, 30, 50, 75, 100, respectively

```{r, echo=FALSE}
n = c(20, 30, 50, 75, 100)
q = pnorm((8.25-0.4*n) / sqrt(0.4*0.6*n))
q
```
## (iii)
```{r, echo=FALSE}
x=0:8
n=c(20,30,50,100)
p=matrix(0,nrow=4,ncol=9)
for(i in 1:4)
{
  for(j in 1:9)
  {
    p[i,j]=choose(n[i],x[j])*(0.4)^x[j]*(1-0.4)^{n[i]-x[j]}
  }
}
t1=sum(p[1,])
t2=sum(p[2,])
t3=sum(p[3,])
t4=sum(p[4,])
t=c(t1,t2,t3,t4)
t
q=pnorm((8.25-0.4*n)/sqrt(0.4*0.6*n))
q
plot(n,t-q,lwd=2,col=2,xlab="n",ylab="error")
```

## (iv)

  The error plots shows that as N gets greater the error decreases, and when N=50 the approximation holds up well
because the error is low.

## Problem 2
## (i)
```{r, echo=FALSE}
rm(list=ls(all=TRUE))
P=c() ; Q=c()
for (i in 1:100) {
  n = 20
  X = rnorm(n, 2, 3)
  P[i] = (mean(X) - 2) / (sqrt(3^2/n))
  Q[i] = ((n-1)*var(X))/3^2
}
par(mfrow=c(1,3))
plot(density(P))
plot(density(Q))
plot(P, Q, main="Scatter Plot")
```

## (ii)
```{r, echo=FALSE}
rm(list=ls(all=TRUE))
P=c() ; Q=c()
for (i in 1:100) {
  n = 30
  X = rnorm(n, 2, 3)
  P[i] = (mean(X) - 2) / (sqrt(3^2/n))
  Q[i] = ((n-1)*var(X))/3^2
}
par(mfrow=c(1,3))
plot(density(P))
plot(density(Q))
plot(P, Q, main="Scatter Plot")
```

## (iii)
```{r, echo=FALSE}
rm(list=ls(all=TRUE))
P=c() ; Q=c()
for (i in 1:100) {
  n = 50
  X = rnorm(n, 2, 3)
  P[i] = (mean(X) - 2) / (sqrt(3^2/n))
  Q[i] = ((n-1)*var(X))/3^2
}
par(mfrow=c(1,3))
plot(density(P))
plot(density(Q))
plot(P, Q, main="Scatter Plot")
```

## (iv)
```{r, echo=FALSE}
rm(list=ls(all=TRUE))
P=c() ; Q=c()
for (i in 1:100) {
  n = 75
  X = rnorm(n, 2, 3)
  P[i] = (mean(X) - 2) / (sqrt(3^2/n))
  Q[i] = ((n-1)*var(X))/3^2
}
par(mfrow=c(1,3))
plot(density(P))
plot(density(Q))
plot(P, Q, main="Scatter Plot")
```

## (v)
  The plots of x average - 2 are symmetrical and therefore follows normal distribution.
  The plots of (n - 1) is right skewed and therefore follows chi square distribution.

## (vi)
  The scatter plot shows that there is no association between them, therefore they are independently distributed.
  